Influences of GDP in the U.S

### 2022-11-10 Manuscript/manuscript.tex
commit

% roadmap and contributions

@@

\paragraph{Data}

>>>>

Kalyoncu found that there is "unidirectional causality from per capita GDP to per capita energy consumption for Armenia."(cite dergipark thing). Their research focused on the relationship between energy consumption and economic growth.
The countries they focused their study on, Georgia, Azerbaijan and Armenia from 1995 to 2009, all faced low energy supply. 
% roadmap and contributions

@@

\paragraph{Data}
%Who collected the data (source)?

The economic data used in this research was collected from Federal Reserve Economic Data(FRED). This is an online database that is maintained by the Research Department at the Federal Reserve Bank of St. Louis. 
The energy data used in this research was collected from the U.S. Energy Information Administration website. The EIA "ollects, analyzes, and disseminates independent and impartial energy information to promote sound policymaking, efficient markets, and public understanding of energy and its interaction with the economy and the environment."(EIA)
%How was the data collected? Sampling frame? Sampling approach?

%What period or range does the data cover?

%Why does the data helps answer the research question?

%What exploratory analyses are done (descriptives, visualication, etc.)?
